Tidy data structure to support exploration and modeling of temporal data

### 2018-12-31 main.Rmd
mv fun prog to software design

## Rolling window in functional programming

@@

As the name indicates, `slide()` expects one input, `slide2()` two inputs, and `pslide()` multiple inputs. An arbitrary function can be mapped and rolled over a block of elements given a specified window size. For type stability, the functions always return lists. Other variants including `*_lgl()`, `*_int()`, `*_dbl()`, `*_chr()` return vectors of the corresponding type, as well as `*_dfr()` and `*_dfc()` for row-binding and column-binding data frames respectively. Their multiprocessing equivalents prefixed by `future_` enable rolling in parallel. This family of functions empowers users to incorporate window-related operations in their workflows.

data-centric & human-centered.

@@

>>>>

## Functional programming

@@

The **purrr** package sets a great example of functional programming in R. It provides a complete and consistent set of tools to iterate each element of a vector with a function. Rolling window not just iterates but roll over a sequence of elements, with `slide()`, `tile()` and `stretch()`. `slide()` expects one input, `slide2()` two inputs, and `pslide()` multiple inputs. For type stability, the functions always return lists. Other variants including `*_lgl()`, `*_int()`, `*_dbl()`, `*_chr()` return vectors of the corresponding type, as well as `*_dfr()` and `*_dfc()` for row-binding and column-binding data frames respectively. Their multiprocessing equivalents prefixed by `future_` enable rolling in parallel. This family of functions empowers users to incorporate window-related operations in their workflows.

@@

```{r calendar-plot, fig.height = 7, fig.cap = "(ref:calendar-plot-cap)"}
```

(ref:calendar-plot-cap) Half-hourly average electricity use.
